Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-09-03 draft.tex
modify initial setup in section 2.2.1 to remove non-decisive war

There are three ways to end up in war: either of the parties may attack first, or both may attack simultaneously. We denote the payoffs of war as a lottery $\Omega$.\footnote{Because the unrecognized state already controls territory and the \emph{de facto} borders are armed, there is likely only a small advantage to be gained by attacking first for either side. Therefore, we argue it is not essential to differentiate between these war scenarios analytically.} This lottery determines one of three potential outcomes: outright victory by either of the players, which are both absorbing states, and an indecisive war where costs of war are borne but then the game returns to the status quo in which the game continues to the next period. Outright victory would, among other things, allow an unrecognized state to force recognition by the home state government. Therefore, outright victory requires more than simply securing control of the disputed territory (which the secessionists have already done when the game begins) and requires the ability to impose the terms of settlement. In practice, this likely involves the capture of the home state capital and/or the overthrow of the home state government.

For probabilities $p_1$ of outright victory, $p_2$ of loss and $1-p_1-p_2$ of non-decisive war, player $i \in \{s, g\}$ in period $n$ with a fixed cost of war $\zeta_i$
faces war lottery $ \omega_{in} \equiv (p_1 (W_{in}-\zeta_i), p_2( L_{in}-\zeta_i), (1-p_1-p_2)(Q_{in}-\zeta_i))$. $\Omega_n \equiv (\omega_{gn}, \omega_{sn}).$\footnote{Baseline costs of war are fixed ($\zeta_i$) but additional costs of war based on war's result are captured in $W_i$ and $L_i$.} Players are assumed to approach war lotteries as expected values.

>>>>

There are three ways to end up in war: either of the parties may attack first, or both may attack simultaneously. We denote the payoffs of war as a lottery $\Omega$.\footnote{Because the unrecognized state already controls territory and the \emph{de facto} borders are armed, there is likely only a small advantage to be gained by attacking first for either side. Therefore, we argue it is not essential to differentiate between these war scenarios analytically.} This lottery determines whether the secessionists or government wins the war. For simplicity, we assume the outcome of the war is an absorbing state.\footnote{The model can easily be extended to encompass the possibility of an indecisive war.} Outright victory would, among other things, allow an unrecognized state to force recognition by the home state government. Therefore, outright victory requires more than simply securing control of the disputed territory (which the secessionists have already done when the game begins) and requires the ability to impose the terms of settlement. In practice, this likely involves the capture of the home state capital and/or the overthrow of the home state government.

For probabilities $p_1$ of outright victory and $1-p_1$ of loss, player $i \in \{s, g\}$ in period $n$ with a fixed cost of war $\zeta_i$ faces war lottery $ \omega_{in} \equiv (p_1 (W_{in}-\zeta_i), \left(1-p_1\right)( L_{in}-\zeta_i))$. $\Omega_n \equiv (\omega_{gn}, \omega_{sn}).$\footnote{Baseline costs of war are fixed ($\zeta_i$) but additional costs of war based on war's result are captured in $W_i$ and $L_i$.} Players are assumed to approach war lotteries as expected values.
